---
title: "Project Workflow"
author: "Yang Zhu"
date: "9/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Role and Responsibility

Wenjie Chen \|

HanYu Qi \|

Yang Zhu \|

# Phase 1: Main Tasks

-   Search similar studies: crime incidence prediction, time series model on predicting crime, spatial analysis, Imbalance data.

-   R package/API: weather data source (GTA area)

-   Data source: 2017-2019 GTA neighbourhood population summary

-   Code: Data Joining, preprocessing, exploratory analysis, baseline model

## Week1 action items:

-   Wenjie Chen & HanYu Qi: dplyr:: left\_join, mutate, filter, select, inner\_join, arrange, slice, group\_by, summarise, count tidyr:: pivot\_wider, pivot\_longer, fill

1 Paper about crime incidence/autotheft prediction: Introduce the dataset used, summarise the machine learning/statistical method they used, model performance, limitations.

Wenjie Chen: weather data (R package or API) HanYu Qi: GTA population change rate (Neighbourhood)

-   Yang Zhu:

Technical help on data manipulation process, Data source validation

## Week2 action items:

```{r}
stations_search(coords = c(43.64421, -79.43536), dist = 20, interval = "day")
xxx <- unique(dt$Neighbourhood)
station_id_lst <- c()
for (i in 1:length(xxx)) {
  subset_dt <- dt %>% 
    filter(Neighbourhood == xxx[i]) %>% 
    sample_n(1) %>% 
    select(Long, Lat)
  
  station_id <- stations_search(coords = subset_dt, dist = 10, interval = "day") %>% 
    filter(distance == min(distance)) %>% 
    select(station_id)
  
  station_id_lst <- c(station_id_lst, station_id)
  
}
```
```

-   Wenjie Chen & HanYu Qi: STA130 week3 Problem Set R code

-   HanYu Qi: Mapping Statistics Canada data with the neighborhood in Autotheft data, create a new column called `annual_pop_change_rate`, using `left_join()`. Find a new paper, read and prepare for presentation.

-   Wenjie Chen: Mapping Weather data based on coordinate (latitude, longitude). create a new column called `station_id` by using for loop or manual work. Finish reading paper, prepare for presentation.

## Week3 action items:

```{r}
raw <- tibble(Hood_ID = c(1,1,2,3,3,4), 
              occurance_year = c(2016,2017,2017,2018,2019,2018))
pop_2016 <- tibble(Hood_ID = c(1,2,3,4),
                   pop_2016 = c(110,120,130,140),
                   pop_old_2016 = c(55,34,52,21))
growth_rate_dt <- tibble(Hood_ID = c(1,2,3,4),
                         growth_rate = c(0.05,-0.01,-0.1,0.12))
new <- raw %>% 
  left_join(pop_2016,by="Hood_ID") %>% 
  left_join(growth_rate_dt, by ="Hood_ID") %>% 
  mutate(pop = pop_2016 * (1+growth_rate)^(occurance_year - 2016),
         pop_old = pop_old_2016 * (1+growth_rate)^(occurance_year - 2016))
```

-   HanYu Qi: Mapping Statistics Canada data with the neighborhood in Autotheft data, create a new column called `annual_pop_change_rate`, using `left_join()`. Find a new paper, read and prepare for presentation.

-   Wenjie Chen: #Mapping Weather data based on coordinate (latitude, longitude). create a new column called `station_id` by using for loop or manual work. Left Join weather data by station_id, year, month, day, hour.# look into details of outcome, LFSNBC method and other reference paper. Do presentation on two relavent papers

